\vspace{-1em}Guidance, please! Towards a framework for RDF-based constraint languages.

### 2015-07-07 paper/paper 2/dc-2015.tex
section 2.3

The implementation model of the \emph{RDF-CV} (Figure \ref{fig:RDF-CV-implementation-model}) shows that
both \emph{property constraints} and \emph{class constraints} are \emph{simple constraints}. 
%For both \emph{property} and \emph{class constraints} a \emph{context class}, a list of \emph{classes}, the \emph{constraining element}, and the \emph{constraining value} can be stated. 
%Lists of \emph{left} and \emph{right properties} can only be specified for \emph{property constraints}.
\begin{figure}[H]
	\centering
		\includegraphics[width=0.80\textwidth]{images/RDF-CV-implementation-model.png}
	\caption{\emph{RDF Constraints Vocabulary (RDF-CV)} Implementation Model}
	\label{fig:RDF-CV-implementation-model}
\end{figure}
A \emph{simple constraint} holds for all individuals of their \emph{context class}.
The \emph{minimum qualified cardinality restriction} {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person,}}
which restricts \emph{publications} to have at least one \emph{author} which must be a \emph{person},
is an example of a \emph{property constraint} on \emph{author}
which holds for all individuals of the class \emph{Publication}.
Table \ref{tab:property-constraint-cardinality-restriction} displays the mapping to the \emph{RDF-CV}.
\begin{table}[H]
  \scriptsize
  \sffamily
  \vspace{0cm}
	\caption{Minimum Qualified Cardinality Restriction as Property Constraint}
	\label{tab:property-constraint-cardinality-restriction}
	\centering
		\begin{tabular}{c|c|c|c|c|c|c}
      \textbf{constraint set} & \textbf{context class} & \textbf{left property list} & \textbf{right p. list} & \textbf{classes} & \textbf{constraining element} & \textbf{c. value} \\
      \hline
      property & Publication & author & - & Person & $\geq$ & 1 \\
		\end{tabular}
\end{table}

The \emph{constraining element} indicates the actual type of constraint like \emph{DL} concept and role constructors, (in)equality, and further keywords for constraint types whose constraints cannot be expressed in \emph{DL} (e.g., regular expressions and constraining facets).
In some cases, a constraint is only complete when a \emph{constraining value} is stated in addition to the \emph{constraining element}
and \emph{simple constraints} may refer to a list of \emph{classes}.
The \emph{constraining element} of the \emph{property constraint} {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person},} e.g.,  is the \emph{DL at-least restriction} \emph{$\geq$}, the \emph{constraining value} is \emph{1}, and
the list of \emph{classes} includes \emph{Person} which restricts the objects of the property \emph{author} to be of the class \emph{Person}.
For \emph{property constraints}, \emph{left} and \emph{right property lists} are specified.
The assignment of properties to these lists happens relative to the \emph{constraining element} 
which may be an operator like $\sqsubseteq$.
\emph{Object Property Paths} (\emph{R-55})
ensure that if an individual \emph{x} is connected by a sequence of object properties with an individual \emph{y}, 
then \emph{x} is also related to \emph{y} by a particular object property. 
As \emph{Stephen-Hawking} is the \emph{author} of the book \emph{A-Brief-History-Of-Time} 
%{\small\ms{(authorOf(Stephen-Hawking, A-Brief-History-Of-Time))}} 
whose \emph{genre} is \emph{Popular-Science}, 
%{\small\ms{(genre(A-Brief-History-Of-Time, Popular-Science)),}}
the \emph{object property path} {\small\ms{authorOf $\circ$ genre $\sqsubseteq$ authorOfGenre}} infers that \emph{Stephen-Hawking} is an \emph{author} of the \emph{genre} \emph{Popular-Science}. 
%{\small\ms{(authorOfGenre(Stephen-Hawking, Popular-Science))}.}
Thus, when mapped to the \emph{RDF-CV} (Table \ref{tab:property-constraint-object-property-paths}), the properties \emph{authorOf} and \emph{genre} are placed on the left side of the \emph{constraining element} \emph{$\sqsubseteq$}
and the property \emph{authorOfGenre} on the right side.
As this \emph{property constraint} holds for all individuals within the data, the \emph{context class} is the \emph{DL top concept} $\top$ which stands for the super-class of all classes.
\begin{table}[H]
  \scriptsize
  \sffamily
  \vspace{0cm}
	\caption{Object Property Paths as Property Constraint}
	\label{tab:property-constraint-object-property-paths}
	\centering
		\begin{tabular}{l|l|l|l|l|l|l}
      \textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      \hline
      property & $\top$ & authorOf, genre & authorOfGenre & $\top$ & $\sqsubseteq$ & - \\
		\end{tabular}
\end{table}

>>>>

The implementation model of the \emph{RDF-CV} (Figure \ref{fig:RDF-CV-implementation-model}) shows that
both \emph{property constraints} and \emph{class constraints} are \emph{simple constraints}. 
%For both \emph{property} and \emph{class constraints} a \emph{context class}, a list of \emph{classes}, the \emph{constraining element}, and the \emph{constraining value} can be stated. 
%Lists of \emph{left} and \emph{right properties} can only be specified for \emph{property constraints}.
\begin{figure}[H]
	\centering
		\includegraphics[width=0.80\textwidth]{images/RDF-CV-implementation-model.png}
	\caption{\emph{RDF Constraints Vocabulary (RDF-CV)} Implementation Model}
	\label{fig:RDF-CV-implementation-model}
\end{figure}
A \emph{simple constraint} holds for all individuals of their associated \emph{context class}.
The \emph{minimum qualified cardinality restriction} {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person,}}
which restricts \emph{publications} to have at least one \emph{author} which must be a \emph{person},
is an example of a \emph{property constraint} on \emph{author}
which holds for all individuals of the class \emph{Publication}.
Table \ref{tab:property-constraint-cardinality-restriction} displays how the \emph{property constraint} is generically represented using the \emph{RDF-CV}.
\begin{table}[H]
  \scriptsize
  \sffamily
  \vspace{0cm}
	\caption{Minimum Qualified Cardinality Restriction as Property Constraint}
	\label{tab:property-constraint-cardinality-restriction}
	\centering
		\begin{tabular}{c|c|c|c|c|c|c}
      \textbf{constraint set} & \textbf{context class} & \textbf{left property list} & \textbf{right p. list} & \textbf{classes} & \textbf{constraining element} & \textbf{c. value} \\
      \hline
      property & Publication & author & - & Person & $\geq$ & 1 \\
		\end{tabular}
\end{table}

The \emph{constraining element} indicates the actual type of constraint like \emph{DL} concept and role constructors ($\sqsubseteq$, $\equiv$, $\sqcap$, $\sqcup$, $\neg$, $\exists$, $\forall$, $\geq$, $\leq$), (in)equality (=, $\ne$), and further keywords for constraint types whose constraints cannot be expressed in \emph{DL} (e.g., regular expressions and constraining facets). We provide a complete list of all constraining elements which can be used to express constraints of any constraint type \cite{BoschNolleAcarEckert2015}.

In some cases, a constraint is only complete when a \emph{constraining value} is stated in addition to the \emph{constraining element}
and \emph{simple constraints} may refer to a list of \emph{classes}.
The \emph{constraining element} of the \emph{property constraint} {\small\ms{Publication $\sqsubseteq$ $\geq$1 author.Person},} e.g.,  is the \emph{DL at-least restriction} \emph{$\geq$}, the \emph{constraining value} is \emph{1}, and
the list of \emph{classes} includes \emph{Person} which restricts the objects of the property \emph{author} to be of the class \emph{Person}.
For \emph{property constraints}, \emph{left} and \emph{right property lists} are specified.
The assignment of properties to these lists happens relative to the \emph{constraining element} 
which may be an operator like $\sqsubseteq$.
\emph{Object Property Paths} (\emph{R-55})
ensure that if an individual \emph{x} is connected by a sequence of object properties with an individual \emph{y}, 
then \emph{x} is also related to \emph{y} by a particular object property. 
As \emph{Stephen-Hawking} is the \emph{author} of the book \emph{A-Brief-History-Of-Time} 
%{\small\ms{(authorOf(Stephen-Hawking, A-Brief-History-Of-Time))}} 
whose \emph{genre} is \emph{Popular-Science}, 
%{\small\ms{(genre(A-Brief-History-Of-Time, Popular-Science)),}}
the \emph{object property path} {\small\ms{authorOf $\circ$ genre $\sqsubseteq$ authorOfGenre}} infers that \emph{Stephen-Hawking} is an \emph{author} of the \emph{genre} \emph{Popular-Science}. 
%{\small\ms{(authorOfGenre(Stephen-Hawking, Popular-Science))}.}
Thus, when mapped to the \emph{RDF-CV} (Table \ref{tab:property-constraint-object-property-paths}), the properties \emph{authorOf} and \emph{genre} are placed on the left side of the \emph{constraining element} \emph{$\sqsubseteq$}
and the property \emph{authorOfGenre} on the right side.
As this \emph{property constraint} holds for all individuals within the data, the \emph{context class} is the \emph{DL top concept} $\top$ which stands for the super-class of all classes.
\begin{table}[H]
  \scriptsize
  \sffamily
  \vspace{0cm}
	\caption{Object Property Paths as Property Constraint}
	\label{tab:property-constraint-object-property-paths}
	\centering
		\begin{tabular}{l|l|l|l|l|l|l}
      \textbf{c. set} & \textbf{context class} & \textbf{left p. list} & \textbf{right p. list} & \textbf{classes} & \textbf{c. element} & \textbf{c. value} \\
      \hline
      property & $\top$ & authorOf, genre & authorOfGenre & $\top$ & $\sqsubseteq$ & - \\
		\end{tabular}
\end{table}
